### 2016-03-14 paper3.tex
Framed telfit within thesis better.

\chapter{Correcting for Telluric Absorption: Methods, Case Studies, and Release of the TelFit Code}
\label{chap:telfit}
This chapter was previously published \citep{Gullikson2014}. Both co-authors were my advisor at some point while I was developing this code. They helped guide the code requirements and provided a science case study for the work. Adam Kraus provided observational data for the case study.

@@

In this paper we describe Telfit\footnote{The TelFit code is available for download from \url{www.as.utexas.edu/~kgulliks/projects.html}}, a code that acts as a wrapper to LBLRTM and allows for easy fitting of the telluric spectrum in astronomical data. We compare the results to those obtained from empiricial telluric correction in optical echelle spectra, and find that model-fitting produces similar telluric line residuals and is in fact better for dim targets or high signal-to-noise ratio work. We only demonstrate the use of TelFit in optical spectra in this work, but note that an earlier version of this code corrected telluric methane absorption near $2.3 \mu$m to $\sim 5\%$ of the continuum level \citep{Gullikson2013}. \cite{Seifahrt2011} provide a case study of telluric modeling in several bands in the near-infrared using a different code, and find similar results.

We describe the observations and data reduction used in this paper in Section \ref{paper3_sec:obs}. We then describe the TelFit code and give a brief description of the telluric fitting procedure in Section \ref{paper3_sec:tellcorr}. Finally, we demonstrate the use of the TelFit code to correct several optical telluric bands in Section \ref{paper3_sec:results}.

>>>>

\chapter{Correcting for Telluric Absorption: Methods, Case Studies, and the TelFit Code}
\label{chap:telfit}
This chapter was previously published \citep{Gullikson2014}. Both co-authors were my advisor at some point while I was developing this code. They helped guide the code requirements and provided a science case study for the work. Adam Kraus provided observational data for the case study.

@@

Telluric correction is vital to the work described in this thesis. In the optical, it allows us to use more of the spectrum to search for faint companions. Importantly, the red parts of the optical spectrum that are most affected by telluric contamination are where the primary-to-secondary flux ratio is smallest, and so where much of the companion-detecting power lies. Telluric correction is even more important in near-infrared spectra, where the contamination dominates at almost all wavelengths.

In this chapter we describe Telfit\footnote{The TelFit code documentation and installation directions can be found at \url{http://telfit.readthedocs.org/en/latest/}}, a code that acts as a wrapper to LBLRTM and allows for easy fitting of the telluric spectrum in astronomical data. We compare the results to those obtained from empiricial telluric correction in optical echelle spectra, and find that model-fitting produces similar telluric line residuals and is in fact better for dim targets or high signal-to-noise ratio work. We only demonstrate the use of TelFit in optical spectra in this work, but note that we use it to accurately remove the telluric contamination in near-infrared spectra in Chapters \ref{chap:dsd} and \ref{chap:survey}, and use an earlier version of TelFit in Chapter \ref{chap:pilot}

We describe the observations and data reduction used in this chapter in Section \ref{paper3_sec:obs}. We then describe the TelFit code and give a brief description of the telluric fitting procedure in Section \ref{paper3_sec:tellcorr}. Finally, we demonstrate the use of the TelFit code to correct several optical telluric bands in Section \ref{paper3_sec:results}.
